\documentclass{article}

\begin{document}

\subsection*{Abstract}
The ALICE experiment consists of a central barrel and a forward muon spec-
trometer. Additional smaller detectors for global event characterization and
triggering are located at small angles outside of the central barrel. Such a ge-
ometry allows the investigation of many properties of diffractive reactions at
hadron colliders for example the measurement of single and double diffractive
dissociation cross-sections and the study of central exclusive production (CEP).
Central diffractive events are defined experimentally by hits in the central barrel
and no activity outside of it creating an activity gap in the rapidity observable.

Studying \emph{Pythia-8} simulations of these processes shows a drastic reduction
of non-diffractive events (background) by enforcing the rapidity gap condition.
The remaining background is largely composed of partially reconstructed CEP
events, so called feed down events. Often feed down events are accompanied
by neutral particles which are not detected. This missing mass and momentum
leads to a shift of the invariant mass spectrum to lower masses. This work
aims at applying machine learning methods for background suppression of CEP
events.

The measured variables \emph{e.g.} the four-momentum of particles, energy loss in
the detectors, deduced kinematic quantities, and global event characteristics are
in general correlated. To obtain a maximal separation of signal and background
it is necessary to treat these observables in a fully multivariate way.

\end{document}
